---
title: "2407 R Script"
output: html_notebook
---

Importing relevant libraries
```{r}
library(data.table)
library(mltools)
library(DMwR)
library(plyr)
library(dplyr)
library(caTools)
library(caret)
library(e1071)
library(corrplot)
library("arules")
library(nnet)
library(randomForest)
library(Boruta)
#install.packages("scales")
library(plotly)
#install.packages('arulesViz')
set.seed(1000)
```

Importing dataset for initial preparation
```{r}
clamp <- fread("ClaMP_Raw-5184.csv")
clamp <- lapply(clamp,  as.numeric)
clamp <- data.frame(clamp)
str(clamp)
```

Remove empty columns
```{r}
clamp$e_res <- NULL
clamp$e_res2 <- NULL
clamp$e_magic <- NULL
clamp$e_crlc <- NULL

row.has.na <- apply(clamp, 1, function(x){any(is.na(x))})
row.with.na <- clamp[row.has.na,]

str(clamp)
```
Based on the structure observed, we add and rename columns to make dataset more relevant for Tesla
```{r}
# Rename columns
colnames(clamp)[which(names(clamp) == "ImageBase")] <- "ChargeCycles"
colnames(clamp)[which(names(clamp) == "SizeOfImage")] <- "CarMileage"
colnames(clamp)[which(names(clamp) == "CreationYear")] <- "YearObtained"
colnames(clamp)[which(names(clamp) == "MajorSubsystemVersion")] <- "SoftwareVersion"
colnames(clamp)[which(names(clamp) == "MinorSubsystemVersion")] <- "OSVersion"
colnames(clamp)[which(names(clamp) == "Machine")] <- "Models"
colnames(clamp)[which(names(clamp) == "class")] <- "MalwareDetection"

# Adding in new column
teslacountries <- fread("TeslaCountries.csv")
clamp <- clamp %>% left_join(teslacountries, by = c("e_lfanew" = "CountryID"))
clamp$e_lfanew <- NULL
#clamp$Country <- as.factor(clamp$Country)
```

Converting to numeric columns
```{r}
clamp_num_names <- c("NumberOfSections", "NumberOfSymbols", "SizeOfOptionalHeader", "ChargeCycles",  "SizeOfInitializedData", "SizeOfUninitializedData", "AddressOfEntryPoint", "BaseOfCode", "BaseOfData", "SizeOfCode", "CarMileage", "SizeOfHeaders", "CheckSum", "SizeOfStackReserve", "SizeOfStackCommit", "SizeOfHeapReserve", "SizeOfHeapCommit", "NumberOfRvaAndSizes")
clamp_num <- clamp[names(clamp) %in% clamp_num_names]
num_names <- names(clamp_num)
clamp_num <- lapply(clamp_num, as.numeric)
clamp_num <- data.frame(clamp_num)
str(clamp_num)
```

Converting the remaining to categorical columns
```{r}
clamp_cat <- clamp
clamp_cat[, num_names] <- list(NULL)
clamp_cat <- lapply(clamp_cat, factor)
clamp_cat <- data.frame(clamp_cat)
str(clamp_cat)
```

Rename factor values (How to hide the revalue results?)
```{r}
clamp_cat$Models <- revalue(clamp_cat$Models, c("332"="Model X", "448"="Model Y", '34404'= 'Model S'))
clamp_cat$OSVersion <- revalue(clamp_cat$OSVersion, c("0"="V5", "1"="V4", '2'= 'V3', '10' = 'V2', '20' = 'V1'))
```


Final dataset
```{r}
clamp_model <- data.frame(clamp_cat, clamp_num)
str(clamp_model)
fwrite(clamp_model, file="TableauClampData.csv")
names(clamp_model)
clamp_corr <- clamp_model
clamp_corr <- data.frame(lapply(clamp_corr, as.numeric))
corrplot(cor(clamp_corr), type = "upper", title = "Correlation Plot for Final Dataset", mar=c(0,0,1,0),
         tl.cex=0.5,
         tl.col = "black")
str(clamp_model)
```

Data visualisation
Numerical variables: Univariate histogram analysis
```{r}
clamp_num1 <- clamp_model[, c("NumberOfSections", "NumberOfRvaAndSizes", "SizeOfOptionalHeader")]
ggplot(melt(clamp_num1), aes(x = value)) + 
    facet_wrap(~ variable, scales = "free") + 
    geom_histogram(binwidth = 1, fill = "indianred3", colour="black")+
    theme_minimal()+
    labs(x = "Factors", y = "Distribution", title = "Histogram of X Factors Part 1") +
    theme(plot.title = element_text(hjust = 0.4))

clamp_num2 <- clamp_model[, c("ChargeCycles", "SizeOfInitializedData", "SizeOfUninitializedData")]
ggplot(melt(clamp_num2), aes(x = value)) + 
    facet_wrap(~ variable, scales = "free") + 
    geom_histogram(binwidth = 1000000, fill = "indianred3", colour="black")+
    theme_minimal()+
    labs(x = "Factors", y = "Distribution", title = "Histogram of X Factors Part 2") +
    theme(plot.title = element_text(hjust = 0.4))

clamp_num3 <- clamp_model[, c("AddressOfEntryPoint", "BaseOfCode", "BaseOfData")]
ggplot(melt(clamp_num3), aes(x = value)) + 
    facet_wrap(~ variable, scales = "free") + 
    geom_histogram(binwidth = 1000000, fill = "indianred3", colour="black")+
    theme_minimal()+
    labs(x = "Factors", y = "Distribution", title = "Histogram of X Factors Part 3") +
    theme(plot.title = element_text(hjust = 0.4))


clamp_num4 <- clamp_model[, c("SizeOfCode", "CarMileage", "SizeOfHeaders")]
ggplot(melt(clamp_num4), aes(x = value)) + 
    facet_wrap(~ variable, scales = "free") + 
    geom_histogram(binwidth = 1000000, fill = "indianred3", colour="black")+
    theme_minimal()+
    labs(x = "Factors", y = "Distribution", title = "Histogram of X Factors Part 4") +
    theme(plot.title = element_text(hjust = 0.4))

clamp_num5 <- clamp_model[, c("CheckSum", "SizeOfStackReserve", "SizeOfStackCommit")]
ggplot(melt(clamp_num5), aes(x = value)) + 
    facet_wrap(~ variable, scales = "free") + 
    geom_histogram(binwidth = 1000000, fill = "indianred3", colour="black")+
    theme_minimal()+
    labs(x = "Factors", y = "Distribution", title = "Histogram of X Factors Part 5") +
    theme(plot.title = element_text(hjust = 0.4))

clamp_num6 <- clamp_model[, c("SizeOfHeapReserve", "SizeOfHeapCommit", "NumberOfSymbols")]
ggplot(melt(clamp_num6), aes(x = value)) + 
    facet_wrap(~ variable, scales = "free") + 
    geom_histogram(binwidth = 10000, fill = "indianred3", colour="black")+
    theme_minimal()+
    labs(x = "Factors", y = "Distribution", title = "Histogram of X Factors Part 6") +
    theme(plot.title = element_text(hjust = 0.4))
```

Numerical variables: Univariate density analysis
```{r}
ggplot(melt(clamp_num1), aes(x = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=1) +
  geom_density(fill = "indianred3")+
  theme_minimal()+
  labs(x = "Factors", y = "Density", title = "Density Plot of X Factors Part 1") +
  theme(plot.title = element_text(hjust = 0.4))

ggplot(melt(clamp_num2), aes(x = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=1) +
  geom_density(fill = "indianred3")+
  theme_minimal()+
  labs(x = "Factors", y = "Density", title = "Density Plot of X Factors Part 2") +
  theme(plot.title = element_text(hjust = 0.4))

ggplot(melt(clamp_num3), aes(x = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=1) +
  geom_density(fill = "indianred3")+
  theme_minimal()+
  labs(x = "Factors", y = "Density", title = "Density Plot of X Factors Part 3") +
  theme(plot.title = element_text(hjust = 0.4))

ggplot(melt(clamp_num4), aes(x = value)) + 
  facet_wrap(~  variable, scales = 'free', ncol=1) +
  geom_density(fill = "indianred3")+
  theme_minimal()+
  labs(x = "Factors", y = "Density", title = "Density Plot of X Factors Part 4") +
  theme(plot.title = element_text(hjust = 0.4))

ggplot(melt(clamp_num5), aes(x = value)) + 
  facet_wrap(~  variable, scales = 'free', ncol=1) +
  geom_density(fill = "indianred3")+
  theme_minimal()+
  labs(x = "Factors", y = "Density", title = "Density Plot of X Factors Part 5") +
  theme(plot.title = element_text(hjust = 0.4))

ggplot(melt(clamp_num6), aes(x = value)) + 
  facet_wrap(~  variable, scales = 'free', ncol=1) +
  geom_density(fill = "indianred3")+
  theme_minimal()+
  labs(x = "Factors", y = "Density", title = "Density Plot of X Factors Part 6") +
  theme(plot.title = element_text(hjust = 0.4))
```

Numerical analysis: Correlation plot
```{r}
corrData <- copy(clamp_model)
corrData$MalwareDetection <- as.numeric(factor(corrData$MalwareDetection, levels = c("0", "1"), exclude = NULL))
# Correlation Matrix
corrDataNum = corrData[, lapply(corrData, is.numeric) == TRUE ]
corrplot(cor(corrDataNum), type = "upper", title = "Correlation Plot for Numeric Data", mar=c(0,0,1,0),
         tl.cex=0.5,
         tl.col = "black")
```

Categorical variables: Univariate barplot analysis
```{r}
ClampCat1= clamp_model[, c("e_cblp", "e_cp", "e_cparhdr","e_minalloc", "e_maxalloc")]
ggplot(melt(ClampCat1, id.vars="e_maxalloc"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 1") +
  theme(plot.title = element_text(hjust = 0.5))

ClampCat2= clamp_model[, c("e_maxalloc", "e_ss", "e_sp","e_csum", "e_ip")]
ggplot(melt(ClampCat2, id.vars="e_ip"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 2") +
  theme(plot.title = element_text(hjust = 0.5))

ClampCat3= clamp_model[, c("e_ip", "e_cs", "e_lfarlc","e_ovno", "e_oemid")]
ggplot(melt(ClampCat3, id.vars="e_oemid"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 3") +
  theme(plot.title = element_text(hjust = 0.5))

ClampCat4= clamp_model[, c("e_oemid", "e_oeminfo", "Models", "Magic", "PointerToSymbolTable")]
ggplot(melt(ClampCat4, id.vars="PointerToSymbolTable"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 4") +
  theme(plot.title = element_text(hjust = 0.5))

ClampCat5= clamp_model[, c("PointerToSymbolTable", "SectionAlignment", "FileAlignment","MajorOperatingSystemVersion", "MinorOperatingSystemVersion")]
ggplot(melt(ClampCat5, id.vars="MinorOperatingSystemVersion"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 5") +
  theme(plot.title = element_text(hjust = 0.5))

ClampCat6= clamp_model[, c("MinorOperatingSystemVersion", "SoftwareVersion", "OSVersion","Subsystem", "LoaderFlags")]
ggplot(melt(ClampCat6, id.vars="LoaderFlags"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 6") +
  theme(plot.title = element_text(hjust = 0.5))

ClampCat7= clamp_model[, c("LoaderFlags", "MalwareDetection", "Country")]
ggplot(melt(ClampCat7, id.vars="Country"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 7") +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(clamp_model, aes(x = YearObtained)) + 
  geom_bar(fill = "indianred3", colour="black", width = 0.5, position = position_dodge(width = 5)) +
  labs(x = "Outcome", 
       y = "Count", 
       title = "Barplot of Year of Origination Distribution") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), plot.title = element_text(hjust = 0.5))

ggplot(clamp_model, aes(x = Characteristics)) + 
  geom_bar(fill = "indianred3", colour="black", width = 0.5, position = position_dodge(width = 5)) +
  labs(x = "Outcome", 
       y = "Count", 
       title = "Barplot of Characteristics Distribution") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), plot.title = element_text(hjust = 0.5))

ClampCat8= clamp_model[, c("MajorLinkerVersion", "MinorLinkerVersion", "MajorImageVersion")]
ggplot(melt(ClampCat8, id.vars="MajorImageVersion"), aes(y = value)) + 
  facet_wrap(~ variable, scales = "free", ncol=2) +
  geom_bar(fill = "indianred3", 
           color="black")+
  theme_minimal()+
  theme(text = element_text(size=10))+
  labs(x = "Factors", y = "Levels", title = "Barplot of Categorical X Factors Part 8") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), plot.title = element_text(hjust = 0.5))

ggplot(clamp_model, aes(x = MajorImageVersion)) + 
  geom_bar(fill = "indianred3", colour="black", width = 0.5, position = position_dodge(width = 5)) +
  labs(x = "Outcome", 
       y = "Count", 
       title = "Barplot of MajorImageVersion Distribution") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), plot.title = element_text(hjust = 0.5))

ggplot(clamp_model, aes(x = MinorImageVersion)) + 
  geom_bar(fill = "indianred3", colour="black", width = 0.5, position = position_dodge(width = 5)) +
  labs(x = "Outcome", 
       y = "Count", 
       title = "Barplot of MinorImageVersion Distribution") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), plot.title = element_text(hjust = 0.5))

ggplot(clamp_model, aes(x = DllCharacteristics)) + 
  geom_bar(fill = "indianred3", colour="black", width = 0.5, position = position_dodge(width = 5)) +
  labs(x = "Outcome", 
       y = "Count", 
       title = "Barplot of DllCharacteristics Distribution") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), plot.title = element_text(hjust = 0.5))

ggplot(clamp_model, aes(x = Country)) + 
  geom_bar(fill = "indianred3", colour="black", width = 0.5, position = position_dodge(width = 5)) +
  labs(x = "Outcome", 
       y = "Count", 
       title = "Barplot of Country Distribution") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), plot.title = element_text(hjust = 0.5))
```

Bivariate analysis
```{r} 
# Malware Detection against Country (Proportion)
plotdata <- clamp_model %>%
  group_by(Country, MalwareDetection) %>%
  dplyr::summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

ggplot(plotdata, aes(fill=factor(plotdata$MalwareDetection), y=n, x=Country, group = Country)) + 
   geom_bar(width = 0.5, position="fill", stat="identity")+
   theme(axis.text.x = element_text(angle = 90, hjust=1), plot.title = element_text(hjust = 0.5))+
  labs(x = "Country", y = "Proportion", title = "MalwareDetection by Country", fill="Malware Detected")

# Malware Detection against Year (Proportion)
plotdata1 <- clamp_model %>%
  group_by(YearObtained, MalwareDetection) %>%
  dplyr::summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

ggplot(plotdata1, aes(fill=factor(plotdata1$MalwareDetection), y=n, x=YearObtained, group = YearObtained)) + 
   geom_bar(width = 0.5, position="fill", stat="identity") +
   theme(axis.text.x = element_text(angle = 90, hjust=1), plot.title = element_text(hjust = 0.5)) +
   labs(x = "Year", y = "Proportion", title = "Malware Detection by Year", fill="Malware Detected")

# Malware Detection by Software Version
plotdata2 <- clamp_model %>%
  group_by(SoftwareVersion, MalwareDetection) %>%
  dplyr::summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

ggplot(plotdata2, aes(fill=factor(plotdata2$MalwareDetection), y=n, x=SoftwareVersion, group = SoftwareVersion)) + 
   geom_bar(width = 0.5, position="fill", stat="identity") +
   theme(axis.text.x = element_text(angle = 90, hjust=1), plot.title = element_text(hjust = 0.5)) +
   labs(x = "Software Version", y = "Proportion", title = "Malware Detection by Software Version", fill="Malware Detected")

plotdata3 <- clamp_model %>%
  group_by(OSVersion, MalwareDetection) %>%
  dplyr::summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

ggplot(plotdata3, aes(fill=factor(plotdata3$MalwareDetection), y=n, x=OSVersion, group = OSVersion)) + 
   geom_bar(width = 0.5, position="fill", stat="identity") +
   theme(axis.text.x = element_text(angle = 90, hjust=1), plot.title = element_text(hjust = 0.5)) +
   labs(x = "OS Version", y = "Proportion", title = "Malware Detection by OS Version", fill="Malware Detected")

plotdata4 <- clamp_model %>%
  group_by(Models, MalwareDetection) %>%
  dplyr::summarize(n = n()) %>% 
  mutate(pct = n/sum(n),
         lbl = scales::percent(pct))

ggplot(plotdata4, aes(fill=factor(plotdata4$MalwareDetection), y=n, x= Models, group = Models)) + 
   geom_bar(width = 0.5, position="fill", stat="identity") +
   theme(plot.title = element_text(hjust = 0.5)) +
   labs(x = "Tesla Models", y = "Proportion", title = "Malware Detection by Model", fill="Malware Detected")
```

SMOTE
```{r}
clamp_smoted <- clamp_model
table(clamp_smoted$MalwareDetection)
proportion <- data.frame(table(clamp_smoted$MalwareDetection))
if (proportion$Freq[1]<proportion$Freq[2] | proportion$Freq[2]<proportion$Freq[1]){
  clamp_smoted <- SMOTE(MalwareDetection ~., clamp_smoted, perc.over = 100, k = 5, perc.under = 200)
}
(table(clamp_smoted$MalwareDetection))
```

Association rules: Initial preparation
```{r}
# Functions used in transforming continuous to discrete data
getBreaks <- function(column_name){
  min_value = 0
  max_value = max(column_name)
  interval = (max_value-min_value)/10
  #print(interval)
  breaks = c(seq(min_value, max_value, by=interval))
  breaks <- ceiling(breaks)
  return(breaks) 
}

getLabels <- function(column_name){
  breaks = getBreaks(column_name)
  #print(breaks)
  labels <- c()
  length <- length(breaks)
  #print(length)
  for (x in 0:length){
    #print(x)
    start <- breaks[x]
    oneStep <- x+1
    end <- breaks[oneStep]-1
    #print(start)
    #print(end)
    if (x == length){
      end <- start
      start <- breaks[x-1]
      string <- paste(toString(start), toString(end), sep="-") 
    } else{
      string <- paste(toString(start), toString(end), sep="-") 
    }
    #print(string)
    labels[x] <- string
  }
  #print(labels)
  deleted <- length - 1
  labels <- labels[-deleted]
  return(labels)
} 

#Splitting the continuous columns into intervals to make them discrete by step
clamp_trans <- clamp_model

clamp_nums <- unlist(lapply(clamp_trans, is.numeric))
clamp_nums <- clamp_trans[ , clamp_nums]
names(clamp_nums)

clamp_nums$NumberOfSymbols <- cut(clamp_nums$NumberOfSymbols,
                            breaks = getBreaks(clamp_nums$NumberOfSymbols),
                            labels = getLabels(clamp_nums$NumberOfSymbols),
                            right = FALSE)
clamp_nums$SizeOfStackReserve <- cut(clamp_nums$SizeOfStackReserve,
                            breaks = getBreaks(clamp_nums$SizeOfStackReserve),
                            labels = getLabels(clamp_nums$SizeOfStackReserve),
                            right = FALSE)
clamp_nums$SizeOfInitializedData <- cut(clamp_nums$SizeOfInitializedData,
                            breaks = getBreaks(clamp_nums$SizeOfInitializedData),
                            labels = getLabels(clamp_nums$SizeOfInitializedData),
                            right = FALSE)
clamp_nums$SizeOfStackCommit <- cut(clamp_nums$SizeOfStackCommit,
                            breaks = getBreaks(clamp_nums$SizeOfStackCommit),
                            labels = getLabels(clamp_nums$SizeOfStackCommit),
                            right = FALSE)
clamp_nums$AddressOfEntryPoint <- cut(clamp_nums$AddressOfEntryPoint,
                            breaks = getBreaks(clamp_nums$AddressOfEntryPoint),
                            labels = getLabels(clamp_nums$AddressOfEntryPoint),
                            right = FALSE)
clamp_nums$BaseOfCode <- cut(clamp_nums$BaseOfCode,
                            breaks = getBreaks(clamp_nums$BaseOfCode),
                            labels = getLabels(clamp_nums$BaseOfCode),
                            right = FALSE)
clamp_nums$BaseOfData <- cut(clamp_nums$BaseOfData,
                            breaks = getBreaks(clamp_nums$BaseOfData),
                            labels = getLabels(clamp_nums$BaseOfData),
                            right = FALSE)
clamp_nums$ChargeCycles <- cut(clamp_nums$ChargeCycles,
                            breaks = getBreaks(clamp_nums$ChargeCycles),
                            labels = getLabels(clamp_nums$ChargeCycles),
                            right = FALSE)
clamp_nums$SizeOfHeapReserve <- cut(clamp_nums$SizeOfHeapReserve,
                            breaks = getBreaks(clamp_nums$SizeOfHeapReserve),
                            labels = getLabels(clamp_nums$SizeOfHeapReserve),
                            right = FALSE)
clamp_nums$SizeOfHeapCommit <- cut(clamp_nums$SizeOfHeapCommit,
                            breaks = getBreaks(clamp_nums$SizeOfHeapCommit),
                            labels = getLabels(clamp_nums$SizeOfHeapCommit),
                            right = FALSE)
clamp_nums$CarMileage <- cut(clamp_nums$CarMileage,
                            breaks = getBreaks(clamp_nums$CarMileage),
                            labels = getLabels(clamp_nums$CarMileage),
                            right = FALSE)

clamp_nums_name <- names(clamp_nums)
clamp_trans[, clamp_nums_name] <- list(NULL)
clamp_trans <- data.frame(clamp_trans, clamp_nums)

# Converting to transactional data
for(i in 1:ncol(clamp_trans)) clamp_trans[[i]] <- as.factor(clamp_trans[[i]])
trans <- as(clamp_trans, "transactions")
```

Association rules
```{r}
rules <- apriori(data=trans, parameter=list(supp=0.45,conf = 0.85), appearance = list (default = "lhs", rhs="MalwareDetection=1"))
inspect(head(rules))
rules_dataframe <- as(rules, 'data.frame')
rules_no <- apriori(data=trans, parameter=list(supp=0.40,conf = 0.6), appearance = list (default = "lhs", rhs="MalwareDetection=0"))
inspect(head(rules_no))
rules_dataframe_no <- as(rules_no, 'data.frame')
```

Arules visualisation
```{r}
library(arulesViz)
plot(rules, method='two-key plot')
#plot(rules, method='two-key plot', engine='interactive')
plot(rules, method = "paracoord")
plot(rules_no, method='two-key plot')
```

Normalising data for Neural Networks
```{r}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}
nums <- unlist(lapply(clamp_model, is.numeric))
clamp_num_nn <- clamp_model[ , nums]
normalized <- clamp_num_nn
normalized <- as.data.frame(lapply(normalized, normalize))
#names(mmnums)

clamp_fac_nn <- clamp_model
clamp_fac_nn[, names(clamp_num_nn)] <- list(NULL)
maxmindf <- data.frame(clamp_fac_nn, normalized)
str(maxmindf)

mmtrain <- sample.split(Y = maxmindf$MalwareDetection, SplitRatio = 0.7)
mmtrainset <- subset(maxmindf, mmtrain == T)
mmtestset <- subset(maxmindf, mmtrain == F)
```

Training neural network model
```{r}
nn_model <- nnet(MalwareDetection ~ ., data=mmtrainset, size=22, maxit=50, decay=1.0e-5, MaxNWts=15000)

nn_predicted <- predict(nn_model, newdata=mmtestset, type="class")
confusionMatrix(as.factor(nn_predicted), mmtestset$MalwareDetection)
```

Train test split
```{r}
train <- sample.split(Y = clamp_model$MalwareDetection, SplitRatio = 0.7)
trainset <- subset(clamp_model, train == T)
testset <- subset(clamp_model, train == F)
```

Grid search algorithm and K-fold Cross Validation
```{r}
grid_default <- expand.grid(n.trees = 200,
                           interaction.depth = 1,
                           shrinkage = 0.1,
                           n.minobsinnode = 10)

folds=10
cvIndex <- createFolds(factor(trainset$MalwareDetection), folds, returnTrain = T) #stratified k fold
train_control_log <- trainControl(
  index = cvIndex,
  number = folds,
  method = "cv",
)
```

Logistic Regression
```{r}
logistic <- train(MalwareDetection~., data=trainset, trControl = train_control_log, method = "glm", family=binomial)

logreg_probs <- predict(logistic, newdata = testset, type = 'prob')
threshold <- 0.5
logreg_predicted <- data.table(ifelse(logreg_probs > 0.5, 1, 0))
confusionMatrix(as.factor(logreg_predicted$`1`), testset$MalwareDetection)
```
Checking for multicollinearity 
```{r}
# logistic_check <- glm(MalwareDetection ~., data = trainset, family = binomial)
# car::vif(logistic_check)
# It returns an error: there are aliased coefficients in the model
# This means that we have ran into perfect multicollinearity.
# The column involved is "NumberOfRvaAndSizes" which is removed in feature selection process.
```

Random Forest
```{r}
randomForest_model <- randomForest(
  MalwareDetection ~ .,
  data=trainset,
  tuneGrid = grid_default,
  trControl = train_control
)

rf_predicted <- predict(randomForest_model, newdata = testset)
confusionMatrix(rf_predicted, testset$MalwareDetection)
```

Applying Feature Selection using Boruta
```{r}
boruta <- Boruta(MalwareDetection ~ ., data = clamp_model, doTrace = 2, maxRuns=11)
#print(boruta)
plot(boruta, las = 2, cex.axis = 0.7)
#plotImpHistory(boruta)

bor <- TentativeRoughFix(boruta)
#print(bor)
attStats(bor)
#getSelectedAttributes(bor, withTentative = F)
selected_features <- getSelectedAttributes(bor, withTentative = F) 

clamp_selected <- clamp_model[, selected_features]
clamp_selected$MalwareDetection <- clamp_model$MalwareDetection
```

Normalising numerical data
```{r}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}
nums <- unlist(lapply(clamp_selected, is.numeric))
clamp_num_nn_s <- clamp_selected[ , nums]
normalized <- clamp_num_nn_s
normalized <- as.data.frame(lapply(normalized, normalize))
#names(mmnums)

clamp_fac_nn_s <- clamp_selected
clamp_fac_nn_s[, names(clamp_num_nn_s)] <- list(NULL)
maxmindf_s <- data.frame(clamp_fac_nn_s, normalized)
str(maxmindf_s)

#maxmindf <- maxmindf %>% group_by(HasDetections) %>% sample_frac(.7)
#maxmindf <- one_hot(as.data.table(maxmindf))


mmtrain_s <- sample.split(Y = maxmindf_s$MalwareDetection, SplitRatio = 0.7)
mmtrainset_s <- subset(maxmindf_s, mmtrain == T)
mmtestset_s <- subset(maxmindf_s, mmtrain == F)
```

Training neural network
```{r}
start.time <- Sys.time()
nn_model_s <- nnet(MalwareDetection ~ ., data=mmtrainset_s, size=22, maxit=50, decay=1.0e-5, MaxNWts=15000)

nn_predicted_s <- predict(nn_model_s, newdata=mmtestset_s, type="class")
end.time <- Sys.time()
time.taken <- end.time - start.time
confusionMatrix(as.factor(nn_predicted_s), mmtestset_s$MalwareDetection)


```

Neural Network Graph
```{r}
hiddenNodes <- c(1:30)
accuracy <- c()

for (i in c(1:30)) {
  nn_model <- nnet(MalwareDetection ~ ., data=mmtrainset, size=i, maxit=50, decay=1.0e-5, MaxNWts=15000)
  nn_predicted <- predict(nn_model, newdata=mmtestset, type="class")
  cm <- confusionMatrix(as.factor(nn_predicted), mmtestset$MalwareDetection)
  overall <- cm$overall['Accuracy']
  accuracy[i] <- overall
}

accuracy

plot(hiddenNodes, accuracy, ylab="Model Accuracy", xlab="Number of Hidden Nodes")
lines(hiddenNodes, accuracy)

data <- data.frame(hiddenNodes, accuracy)
names(data) <- c("Number of Hidden Nodes", "Model Accuracy")

f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "Number of Hidden Nodes",
  titlefont = f
)
y <- list(
  title = "Model Accuracy",
  titlefont = f
)
fig <- plot_ly(data, x = ~hiddenNodes, y = ~accuracy, type = 'scatter', mode = 'lines')
fig <- fig %>% layout(xaxis = x, yaxis = y)
fig
```

Train Test Split
```{r}
train_s <- sample.split(Y = clamp_selected$MalwareDetection, SplitRatio = 0.7)
trainset_s <- subset(clamp_selected, train == T)
testset_s <- subset(clamp_selected, train == F)
```

Logistic Regression
```{r}
start.time <- Sys.time()
logistic_selected <- train(MalwareDetection~., data=trainset_s, trControl = train_control_log, method = "glm", family=binomial)

logreg_probs_s <- predict(logistic_selected, newdata = testset_s, type = 'prob')
threshold <- 0.5
logreg_predicted_s <- data.table(ifelse(logreg_probs_s > 0.5, 1, 0))
end.time <- Sys.time()
time.taken <- end.time - start.time
confusionMatrix(as.factor(logreg_predicted_s$`1`), testset_s$MalwareDetection)

```

```{r}
start.time <- Sys.time()
randomForest_model_s <- randomForest(
  MalwareDetection ~ .,
  data=trainset_s,
  tuneGrid = grid_default,
  trControl = train_control
)

rf_predicted_s <- predict(randomForest_model_s, newdata = testset_s)
end.time <- Sys.time()
time.taken <- end.time - start.time
confusionMatrix(rf_predicted_s, testset_s$MalwareDetection)

csvMatrix <- confusionMatrix(rf_predicted_s, testset_s$MalwareDetection)
tocsv <- data.frame(cbind(t(csvMatrix$overall)))
write.csv(tocsv,file="csvMatrix.csv")
```

